General purpose gene annotation using deep learning

### 2020-01-22 paper/main.tex
stuff

\begin{table}[!t]
\processtable{Data group statistics\label{Tab:statistics}} {
\begin{tabular}{@{}lll@{}}
\toprule & EnsemblMetazoa & JGI Phytosome\\
\midrule
Fraction of classes  & 0.6, 0.02, 0.1, 0.2 & 0.6, 0.02, 0.1, 0.2 \\
(Intergenic, UTR, CDS, Intron) & & \\
Geenuff error rate & 0.1 (+- 0.02) & 0.3 (+- 0.02) \\
Average genome size in Gbp& 1.1 (+- 0.5) & 0.3 (+- 0.1) \\
Average gene length & 23000 (+- 5000) & 3370 (+- 50) \\
\botrule
\end{tabular}}{Values are averages across all genomes of a data group}
\end{table}

During data generation, we only queried for the longest transcript of each gene and did not include FASTA sequences that had no functional annotation (explanation why this is a sign of error?). As Geenuff checks the genomic annotations for potential errors like missing UTR sections and marks areas as potentially erroneous, we were able to effectively blank out those bases during training. For the training, we divided each continous genomic sequence into 20.000 or 30.000 bases long subsequences, which are then used as input or label for the neural network. We appended zero padding if the subsequences are not long enough. If a subsequence is fully marked as erroneous, we do not include it in the training or evaluation datasets.

>>>>

\begin{table}[!t]
\processtable{Data group statistics for all data\label{Tab:statistics_all}} {
\begin{tabular}{@{}lll@{}}
\toprule & EnsemblMetazoa & JGI Phytosome\\
\midrule
Fraction of classes  & 0.6, 0.02, 0.1, 0.2 & 0.6, 0.02, 0.1, 0.2 \\
(Intergenic, UTR, CDS, Intron) & & \\
Geenuff error rate & 0.1 (+- 0.02) & 0.3 (+- 0.02) \\
Average genome size in Gbp& 1.1 (+- 0.5) & 0.3 (+- 0.1) \\
Average gene length & 23000 (+- 5000) & 3370 (+- 50) \\
\botrule
\end{tabular}}{Values are averages across all genomes of a data group}
\end{table}

\begin{table}[!t]
\processtable{Data group statistics for our training data\label{Tab:statistics_training}} {
\begin{tabular}{@{}lll@{}}
\toprule & EnsemblMetazoa & JGI Phytosome\\
\midrule
Fraction of classes  & 0.6, 0.02, 0.1, 0.2 & 0.6, 0.02, 0.1, 0.2 \\
(Intergenic, UTR, CDS, Intron) & & \\
Geenuff error rate & 0.1 (+- 0.02) & 0.3 (+- 0.02) \\
Average genome size in Gbp& 1.1 (+- 0.5) & 0.3 (+- 0.1) \\
Average gene length & 23000 (+- 5000) & 3370 (+- 50) \\
\botrule
\end{tabular}}{Values are averages across all genomes of a data group}
\end{table}

During data generation, we only queried for the longest transcript of each gene and did not include FASTA sequences that had no functional annotation (explanation why this is a sign of error?). As Geenuff checks the genomic annotations for potential errors like missing UTR sections and marks areas as potentially erroneous, we were able to effectively blank out those bases during training. For the training, we divided each continous genomic sequence into 20.000 bases long subsequences, which are then used as input or label for the neural network. We appended zero padding if the subsequences are not long enough. If a subsequence is fully marked as erroneous, we do not include it in the training or evaluation datasets.
